### 2023-10-13 5.Conclusions/further.tex
Updated further

Of course the first thing that comes to mind to improve the system and making it actually usable for a real world application would be doing inSitu training. Training within the analog system would mean implementing the backpropagation algorithm. Here, two options are available :

@@

Figure out how to change the values of the weights for the inSitu training. Different from \cref{sec:wei2res}.

@@

\subsubsection{Only change the value of one of the two memristor}%TODO

@@

\subsection{\ac{LSTM} continuous mode}

This would allow to have a real time results and not having to retake the same inputs several times. Basically it would be like %TODO Make graphs

This might be something that already exist that I didn't find anything about.

>>>>

Of course the first thing that comes to mind to improve the system and making it actually usable for a real world application would be doing inSitu training, meaning that the weight training would also be happening on the chip. Training on the chip also means that the weights, hence the memristors in the circuit, need to be changed between each epoch. That requires to have a backpropagation algorithm. Here, two options are available :

@@

In order for the inSitu training to work, the weights also need to change. Future work also also include looking for ways to change the weights in the fastest possible way. Idealy the algorithm won't need to compute the weight to resistance conversion (\cref{sec:wei2res}) and directly know how the change the resistances' values.

@@

\subsubsection{Only change the value of one of the two memristor}

This is a potential idea on how to improve the time it takes to compute a single epoch. Indeed changing the resistance value in a memristor, takes time depending on the type of memristor that is being used. If the weight to resistance is computed the same way as in the thesis (\cref{sec:wei2res}), so that each pair of resistance is centered around the middle point of the memristor's resistance range.

Instead of having to do that, the idea is to only change one of the memristor's internal resistance so that the final weight is still the same. \Cref{eq:wei2res0} needs to be respected in any situation. The memristor's resistances won't be centered (\cref{eq:wei2res1}) anymore.

@@

A potential way to implement that, would be in a two phase plan. First the prediction, and so on until a verification on the predictions can be done. After that the weights are updated based on those previous reviewed results.
